%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/quyvx07}{\Large Vũ Xuân Quý}} & Email : \href{mailto:vuxuanquy07@gmail.com}{vuxuanquy07@gmail.com}\\
  \href{https://github.com/quyvx07}{https://github.com/quyvx07} & Mobile : \href{tel:+84388985972}{+84-388-985-972} \\
  {} & DoB: {24/07/1995} \\
\end{tabular*}


%-----------PROFESSIONAL SUMMARY-----------------
\section{PROFESSIONAL SUMMARY}
  {
    - Have 4 years of experience as a FullStack Developer. \\
    - Backend (BE): Proficiency in Laravel, Nodejs for building robust and efficient server-side applications. \\
    - Frontend (FE): Proficiency in Reactjs, React Native, and Vuejs for developing engaging and responsive user interfaces. \\
    - Have experience in making e-commerce website, PWA, Service Worker, Cache API, Web App Manifest  \\
    - Build static html css based on figma (\href{https://github.com/quyvx07/html-static-build}{LINK}) \\
    - Excellent troubleshooting and communication skills. \\
  }


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RikkeiSoft}{Ha Noi, VN}
      {Software Engineer}{5/2019 - Present}
      \resumeItemListStart
        \resumeItem{Team leader}
          {\\
            -	Provide solutions to the requirements from customers. Clear requirement \\
            -	Develop functions, Fix bugs \\
            -	Planning, esimate task \\
            -	Support member, review code \\
            -	Manage the progress of the task \\
          }
        \resumeItem{Development}
          {\\
            -	Clear requirement \\
            -	Develop functions, Fix bugs \\
          }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{E-commerce}
      {\\
        - \textbf{Project description:}
          Collaborated on the maintenance and development of various E-commerce websites, as well as the creation of new websites based on customer requirements.
          Implemented features and functionality to enhance the user experience and streamline online shopping processes.
            \\
        - \textbf{Client:} Korea \\
        - \textbf{Team size:} 4 \\
        - \textbf{Responsibilities:} Development \\
        - \textbf{Programming Language:} Python, Javascript \\
        - \textbf{Framework:} Nestjs, Nextjs \\
        - \textbf{Platform, server and database:} Postgresql, MongoDB, Graphql \\
      }
    \resumeSubItem{Eging App}
      {\\
        - \textbf{Project description:}
            Synthesize and analyzing data available to project area, date, time have many ink.
            Create a monthly cron job to get data from another database. Data analysis provides a method of statistical prediction of squid population
            Use vue to display the analyzed data\\
        - \textbf{Client:} Japan \\
        - \textbf{Team size:} 2 \\
        - \textbf{Responsibilities:} Team leader \\
        - \textbf{Programming Language:} PHP, Javascript \\
        - \textbf{Framework:} Laravel, Reactjs \\
        - \textbf{Platform, server and database:} Mysql \\
      }
    \resumeSubItem{ManagementProject}
      {\\
        - \textbf{Project description:}
            Developing and maintaining an application that allows users to create customized tools according to their needs,
            with a focus on safety and diversity of features.
            The application is widely used by large companies and is built on a platform similar to low-code.\\
        - \textbf{Client:} Japan\\
        - \textbf{Team size:} 30 \\
        - \textbf{Responsibilities:} Team leader \\
        - \textbf{Programming Language:} Java, Javascript \\
        - \textbf{Framework:} Spring Core, Ractive, Nodejs \\
        - \textbf{Platform, server and database:} Linux, MongoDB \\
      }
    \resumeSubItem{CVG}
      {\\
        - \textbf{Project description:}
            I worked on a large-scale web application project for a Vietnamese company that involved multiple provinces.
            To accommodate the scale of the project, we used a microservices architecture.
            Each website was distributed to its corresponding province, and there was also a central website.
            The complexity arose from synchronizing and transferring data between stores in different provinces.\\
        - \textbf{Client:} Viet Nam\\
        - \textbf{Team size:} 30 \\
        - \textbf{Responsibilities:} Team leader \\
        - \textbf{Programming Language:} PHP, Java, Javascript \\
        - \textbf{Framework:} Laravel, Vuejs, Spring \\
        - \textbf{Platform, server and database:} Linux, Mysql \\
      }
    \resumeSubItem{Car Rental}
      {\\
        - \textbf{Project description:}
            Car rental management and tenants. Car rental registration function through 3 steps: Register information, Car rental with price, car pictures
            \\
        - \textbf{Client:} Japan \\
        - \textbf{Team size:} 20 \\
        - \textbf{Responsibilities:} Development \\
        - \textbf{Programming Language:} PHP, Javascript \\
        - \textbf{Framework:} Laravel, Reactjs, ReactNative \\
        - \textbf{Platform, server and database:} Mysql \\
      }
    \resumeSubItem{Food Delivery}
      {\\
        - \textbf{Project description:}
          Shopping cart and delivery on google.
          Build the application interface, use google map integrated into the application,
          handle the shopping cart part (\href{https://github.com/quyvx07/ShopDemoReactNative}{LINK})
          \\
        - \textbf{Client:} VietNam \\
        - \textbf{Team size:} 4 \\
        - \textbf{Responsibilities:} Development \\
        - \textbf{Programming Language:} PHP, Javascript \\
        - \textbf{Framework:} Laravel, ReactNative \\
        - \textbf{Platform, server and database:} Mysql \\
      }
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
% \section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Codegym Viet Nam}{Ha Noi, VN}
      {CGC-Bootcamp PHP}{1/2019 -- 5/2019}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
